Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
intro p1

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through ecological processes such as
species-specific as trophic interactions and resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among others. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->

>>>>

# Introduction
Our inference regarding the processes underlying ecological patterns
are directly linked to the scale at which they are observed [@Levin_1992;
@Allen_2015]. Animals are influenced across scales, through ecological processes such as
species-specific trophic interactions, resource availability
[@Legendre_1993; @Chave_2013], and global climate and productivity [@Field_2009].
<!-- JWT: I'm not sure exactly what that sentence was trying to say so my edits may not work -->
Multiscale ecology has been integrated into species distribution modelling
[@Elith_2009], habitat selection [@Mayor_2007], and food webs [@Sugihara_1989],
among other processes. Meanwhile, in the context of animal behaviour, certain behaviours
are scale-dependent; for example, acoustic communication in birds varies with
spatial scales [@Luther_2009]. We posit that it is important to consider that
animal behaviour within the social environment will be scale-dependent. 
<!-- QW: I think this last sentence needs to be a bit stronger. Why is it important? -->
